\Large{All in the family:\\German twin finishing times in\\the 2016 women's Olympic marathon}

### 2017-02-04 paper/paper.tex
real version sent to scott

The media quickly picked up the Hanher story as an image of the
beaming twins finishing hand-in-hand captured a public audience. While
many believed the moment was a reflection of the Olympic spirit, not
everyone agreed with this rosy interpretation. The twins' happy facial
expressions at the finish were portrayed as a bit contrived---smiling
like ``Honigkuchenpferde,'' cookies in the shape of a horse, was the
description offered by one editorialist---and the sports director of
the German Athletics Federation, Thomas Kurschilgen, stirred up
controversy when he suggested that the Hahners' photo-finish was no
coincidence.  Kurschilgen averred that the twins slowed down so as to
finish simultaneously and create a spectacle which would ``generate
media attention.''  Kurschilgen justified his charge with the fact
that the twins ran the Rio marathon over 18 minutes slower their
personal best times prior to the Olympics.  Kurschilgen's accusations
were denied by the Hahner twins, perhaps not surprisingly, who claimed
that their simultaneous finish was simply an unintended coincidence.

>>>>

The media quickly picked up the Hanher story as an image of the
beaming twins, finishing hand-in-hand, captured a public
audience. While many believed the twin's near-simultaneous finish was
a reflection of Olympic spirit, not everyone agreed with this rosy
interpretation. The twins' happy facial expressions at the finish were
portrayed as a bit contrived---smiling like ``Honigkuchenpferde,''
cookies in the shape of a horse, was the description offered by one
editorialist---and the sports director of the German Athletics
Federation, Thomas Kurschilgen, stirred up controversy when he
suggested that the Hahners' photo-finish was no coincidence.
Kurschilgen averred that the twins slowed down so as to finish
simultaneously and create a spectacle which would ``generate media
attention.''  Kurschilgen justified his charge with the fact that the
twins ran the Rio marathon over 18 minutes slower their personal best
times prior to the Olympics.  Kurschilgen's accusations were denied by
the Hahner twins, perhaps not surprisingly, who claimed that their
joint finish was simply a fortuitous coincidence.
